IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-07 paper/related.tex
presentational issue from reviewer 1
reviewer 1 grammar/spelling

One information flow control technique designed to handle legacy code is
secure multi-execution (SME)~\cite{Devriese:2010}. It runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Authors often present
SME considering one specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language is hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
about which nothing is known except what is inferred from their I/O interactions
with the environment. Similar to SME, our approach mediates I/O
operations; however, our approach only runs the program once.

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in less false alarms and target legacy code, it comes at the
cost of complexity (the system must accommodate the entirety of JavaScript's
semantics~\cite{JSFlow}).
%Moreover, the runtime performance cost are sometimes too high, e.g.,
%higher than 100\%~\cite{JSFlow}.
Alternatively, coarse-grained
approaches to security have also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

@@

The constructs in our IFC language, as well as the behavior of
inter-thread communication, is reminiscent of distributed systems
like Erlang~\cite{Armstrong03makingreliable}.  There is a close
correspondence: in distributed systems, isolation is required due to
physical constraints; in information flow control, isolation is
required to enforce noninterference.  Papagiannis et al.~\cite{Papagiannis_enforcinguser}
built an information flow control system on top of Erlang which is quite
similar to ours.  However, they do not use a floating label system (processes
can find out when sending a message failed due to a forbidden information flow),
and they include no security proofs.

There appears to be limited literature in general techniques for retrofitting
information flow control to arbitrary languages; however, one time-honored
technique is defining a fundamental calculus, for which other languages can be
desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
dependency by showing how various previous systems can be encoded in it; Tse and
Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be
encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
encodes several IFC systems into Paralocks.  However, this line of work is
primarily focused on static enforcements.
%information flow control systems.

>>>>

One information flow control technique designed to handle legacy code is
secure multi-execution (SME)~\cite{Devriese:2010}. It runs
multiple copies of the program, one per security level, where the semantics of
I/O interactions is altered. Authors often present
SME considering one specific programming
language~\cite{KULeuven-350547,Rafnson:2013}. However, Bielova et
al.~\cite{Biel-etal-11-TR} uses a transition system to describe SME, where the
details of the underlying language is hidden.  Zanarini et
al.~\cite{ZanariniJR13} propose a novel semantics for programs based on
interaction trees~\cite{jacobs-tutorial}, which treats programs as black-boxes
about which nothing is known except what is inferred from their I/O interactions
with the environment. Similar to SME, our approach mediates I/O
operations; however, our approach only runs the program once.

One of the primary motivations behind this paper is constructing a practical
information flow control system for JavaScript.  Some of these systems attempt
to perform fine-grained information flow control of
JavaScript~\cite{Hedin:2012,ConDOM,JSFlow}. While fine-grained information flow
control can result in fewer false alarms and target legacy code, it comes at the
cost of complexity (the system must accommodate the entirety of JavaScript's
semantics~\cite{JSFlow}).
%Moreover, the runtime performance cost are sometimes too high, e.g.,
%higher than 100\%~\cite{JSFlow}.
Alternatively, coarse-grained
approaches to security have also been proposed for the web
scenario~\cite{Yip:2009:PBS,DeGroef:2012,conf/esorics/AkhaweLHSS13}.

@@

The constructs in our IFC language, as well as the behavior of
inter-thread communication, are reminiscent of distributed systems
like Erlang~\cite{Armstrong03makingreliable}.  There is a close
correspondence: in distributed systems, isolation is required due to
physical constraints; in information flow control, isolation is
required to enforce noninterference.  Papagiannis et al.~\cite{Papagiannis_enforcinguser}
built an information flow control system on top of Erlang which is quite
similar to ours.  However, they do not use a floating label system (processes
can find out when sending a message failed due to a forbidden information flow),
and they include no security proofs.

There appears to be limited literature in general techniques for retrofitting
information flow control to arbitrary languages; however, one time-honored
technique is defining a fundamental calculus, for which other languages can be
desugared into.  Abadi et al.~\cite{abadi+:core} motivate their core calculus of
dependency by showing how various previous systems can be encoded in it; Tse and
Zdancewic~\cite{Tse:Zdancewic:ICFP04}, in turn, show how this calculus can be
encoded in System F via parametricity.  Broberg and Sands~\cite{Broberg:2010}
encode several IFC systems into Paralocks.  However, this line of work is
primarily focused on static enforcements.
%information flow control systems.

### 2015-01-07 paper/retrofit.tex
reviewer 1 grammar/spelling

Before moving on to the formal treatment of our system, we'd like to give
a brief primer of information flow control and describe some example programs
in our system, emphasizing the parallel between their implementation
in a multi-task setting, and the traditional, ``monolithic'' programming
language feature they simulate.

@@

Our design principles suggests a different resolution: when these
constructs are treated as isolated tasks, each of which have their own heaps, it
is obviously the case that there is no sharing; in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
not be shared, the two systems are morally equivalent. (We elaborate on
this formally in Section~\ref{sec:concrete}.)  Finally, these
semantics strongly suggest that one should restrict the types of
data which may be passed between tasks (for example, in JavaScript, one
might only allow JSON objects to be passed between tasks, rather than
general object structures).

@@

Our goal now is to
describe how to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for the core part of COWL~\cite{swapi}.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references and fixpoint in place of ECMAScript, to demonstrate some of the key
properties without having too much detail (and because the embedding really
does not care about what, exactly, is in the target language); we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

@@

These operations are all defined with respect to an evaluation context
|curlyBlueE| that represents the context of the current task which, by
conventions is running. The evaluation context has three important pieces of
state: the global message queues |iS|, the current label |il| and the task ID |id|.

We note that first class labels, tasks (albeit named differently), and
operations for inspecting the current label are essentially universal to
all floating-label systems.
%
However, our choice of communication primitives is motivated by
those present in browsers, namely \texttt{postMessage}~\cite{webmessaging}.
%
Of course, other choices, such as blocking communication or labeled channels,
are possible. %(see Section~\ref{sec:extensions}).
%

These asynchronous communication primitives are worth further
discussion.  When a task is sending a message using |send|, it also labels that
message with a label |il'| (which must be above the tasks current label |il|).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
$|recvf ix1 ix2 ie1 ie2|$
binds the message and the sender's task identifier
to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
Otherwise, if there are no messages, that tasks continues its execution with |ie2|.
We denote the filtering of the message queue by |filter il Q|,
which is defined as follows.
If |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|, and otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more sensitive
than their current label would allow.

@@

\subsection{The Embedding}
Fig.~\ref{fig:embedding}
provides all of the rules responsible for actually carrying out the embedding of the IFC language with the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of
      both languages to allow for embeddings terms in one language to
      be embedded in the other, as
      in~\cite{Matthews:2007:OSM:1190216.1190220}.
    %
In the target language, an IFC expression appears as |TI ie| (``\Red{T}arget-outside,
IFC-inside''); in the IFC language, a target language expression appears as |IT
te| ( ``{\color{blue}{I}}FC-outside, target-inside'').
    \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.  These rules only operate on the first task in the task list, which by convention is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.  The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|.
    Fig.~\ref{fig:scheduler} defines two concrete schedulers.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
    and intermediating between the borders of the two languages.
\end{itemize}

>>>>

Before moving on to the formal treatment of our system, we give
a brief primer of information flow control and describe some example programs
in our system, emphasizing the parallel between their implementation
in a multi-task setting, and the traditional, ``monolithic'' programming
language feature they simulate.

@@

Our design principles suggest a different resolution: when these
constructs are treated as isolated tasks, each of which have their own heaps, it
is obviously the case that there is no sharing; in fact, the sandboxed task receives a dangling pointer.  Even if there is only one heap, if we enforce that references
not be shared, the two systems are morally equivalent. (We elaborate on
this formally in Section~\ref{sec:concrete}.)  Finally, this
semantics strongly suggests that one should restrict the types of
data which may be passed between tasks (for example, in JavaScript, one
might only allow JSON objects to be passed between tasks, rather than
general object structures).

@@

Our goal now is to
describe how to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for the core part of COWL~\cite{swapi}.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references and fixpoint in place of ECMAScript, to demonstrate some of the key
properties without including too much detail (and because the embedding really
does not care about what, exactly, is in the target language); we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

@@

These operations are all defined with respect to an evaluation context
|curlyBlueE| that represents the context of the current task which.
The evaluation context has three important pieces of
state: the global message queues |iS|, the current label |il| and the task ID |id|.

We note that first-class labels, tasks (albeit named differently), and
operations for inspecting the current label are essentially universal to
all floating-label systems.
%
However, our choice of communication primitives is motivated by
those present in browsers, namely \texttt{postMessage}~\cite{webmessaging}.
%
Of course, other choices, such as blocking communication or labeled channels,
are possible. %(see Section~\ref{sec:extensions}).
%

These asynchronous communication primitives are worth further
discussion.  When a task is sending a message using |send|, it also labels that
message with a label |il'| (which must be above the task's current label |il|).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
$|recvf ix1 ix2 ie1 ie2|$
binds the message and the sender's task identifier
to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
Otherwise, if there are no messages, that task continues its execution with |ie2|.
We denote the filtering of the message queue by |filter il Q|,
which is defined as follows.
If |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|, and otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more sensitive
than their current label would allow.

@@

\subsection{The Embedding}
Fig.~\ref{fig:embedding}
provides all of the rules responsible for actually carrying out the embedding of the IFC language within the target language.
The most important feature of this embedding is that every task maintains its own
copy of the target language global state and evaluation context, thus
enforcing isolation between various tasks.  In more detail:

@@

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of
      both languages to allow for terms in one language to
      be embedded in the other, as
      in~\cite{Matthews:2007:OSM:1190216.1190220}.
    %
In the target language, an IFC expression appears as |TI ie| (``\Red{T}arget-outside,
IFC-inside''); in the IFC language, a target language expression appears as |IT
te| ( ``{\color{blue}{I}}FC-outside, target-inside'').
    \item We reinterpret |CE| to be evaluation contexts on task lists, providing definitions for |curlyRedE| and |curlyBlueE|.  These rules only operate on the first task in the task list, which by convention is the only task executing.
    \item We reinterpret |->|, an operation on a single task, in terms of |.->|, operation on task lists.  The correspondence is simple: a task executes a step and then is rescheduled in the task list according to schedule policy |alpha|.
    Fig.~\ref{fig:scheduler} defines two concrete schedulers.
    \item Finally, we define some rules for scheduling, handling sandboxing tasks (which interact with the state of the target language),
    and intermediating between the borders of the two languages.
\end{itemize}
